Investigating Item Bias 

### 2021-10-27 paper/cogsci.Rmd
The participants section

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(tidyverse)

@@

We analyze American English CDI: Words & Sentences administrations from `r nrow(d_demo)` children aged `r min(d_demo$age)` to `r max(d_demo$age)` from Wordbank [@Frank2016; @Frank2021].

@@

@@

```{r}
sex_tab <- table(d_demo$sex)

eth_tab <- table(d_demo$ethnicity)
```

We use Wordbank data from `r sex_tab["Female"]` female and `r sex_tab["Male"]` male participants, and was unreported for an additional `r sum(is.na(d_demo$sex))` participants.
<!-- same for eth, SES -->

>>>>

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(tidyverse)
library(here)

@@

@@

#Add this exclusion to the Analysis 
removed <- d_demo %>%
  filter(comprehension!=0)
#this is the actually d_demo we used so we must use this in our report
d_demo <- d_demo %>% 
  #filter(comprehension!=0, !is.na(sex)) %>% # can't fit children not producing words, or with NA sex in group model
  arrange(data_id) %>%
  mutate(eth_group = ifelse(ethnicity=="White", "White", "Nonwhite"),
         ses_group = 
           ifelse(is.element(mom_ed, c("None", "Primary", "Some Secondary", "Secondary")), "low", "high"))
```
We analyze American English CDI: Words & Sentences administrations from `r nrow(d_demo)` children aged `r min(d_demo$age)` to `r max(d_demo$age)` from Wordbank [@Frank2016; @Frank2021].

@@

```{r}
sex_tab <- table(d_demo$sex)
ses_tab <- table(d_demo$ses_group)
eth_tab <- table(d_demo$ethnicity)
eth2_tab <- table(d_demo$eth_group)
```

Research was conducted over  `r nrow(d_demo)` participants, whose data was parent reported and collected by the Wordbank Project. Unlike other projects Wordback relies on the kindness of others to contribute their data which means that often meta-data for some sets is missing. Even so, the project now has data over 29 different languages on children from ages 8-30 months old, though our study focused entirely on American English and Children 16-30 months.  When they received complete information, the Wordbank data set collected demographic data consisting of Birth Order, Race/Ethnicity, Sex and Mothers Education. For our study we focused on the comparing data between demographic groups on the axis of Sex, Ethnicity and Mothers Education, which was a proxy for social economic status. Out data included `r sex_tab["Female"]` female and `r sex_tab["Male"]` male participants, and an additional `r sum(is.na(d_demo$sex))` participants whose sex remained unreported. In terms of Ethnicity data was recorded from `r eth_tab["White"]` white, `r eth_tab["Asian"]` Asian, `r eth_tab["Black"]` Black, `r eth_tab["Hispanic"]` Hispanic, and `r eth_tab["Other"]` “Other” participants as well as `r sum(is.na(d_demo$ethnicity))` unreported. Given our distribution of ethnicities, for our analysis we split participants into White (`r eth2_tab["White"]`) and Non-White (`r eth2_tab["Nonwhite"]`). Finally, we split participants into high and low SES, of which we had `r ses_tab["high"]` high SES participants, corresponding to mothers' education of some college or higher and `r ses_tab["low"]` Low SES participants. 
<!-- same for eth, SES -->
